---
title: "R Notebook"
output:
  html_document:
    df_print: paged
name: Ann Gould
github: gould-ann
---


```{r}
data(tips, package="reshape2")
library(dplyr)
library(ggplot2)

```

1. 
```{r}
numParty <- nrow(tips)
print(numParty)
```

2. 
```{r}
print(tips)
print(names(tips))
```
total_bill: total sum of bill: double
tip: tip included: double
size: # of people in party: int
sex: gender of person paying bill: category
smoker: if the person paying bill: category
day: day of the week going out: category
time: specific meal: category

3.
```{r}
newdata <- tips[order(tips$day, decreasing = TRUE),] 
print(newdata)
```

4.
```{r}
female5 <- tips[tips$size >= 5 & tips$sex == "Female",  ]
print(female5)
  
```
5.
```{r}
plot(tips)

```

The lower the bill, the lower the tip typically and vice versa. Linear regression-like line.

6.
There is a lot of data in the lower aspect of the graph, which makes it more difficult to predict later data. There also exists some outliers of people who tip really well/very poorly.

7.
```{r}

tip_rate <- tips$tip / tips$total_bill
data <- tips %>%
  summarise(tiprate = mean(tip)) 

data2 <- tips %>%
  summarise(billrate = mean(total_bill))

avg_tip_rate <- data$tiprate/data2$billrate
print(avg_tip_rate)
```
The rate is: about 15%

8.

```{r}
my_plot <- ggplot(data = tips, aes(x = tips$time, y=tip_rate))
my_plot + geom_boxplot()
```

This shows that the average tips are higher for lunch than they are for dinner, but there are more outliers in the ladder part of the data because the mean line is lower on the lunch line. The dinner tips are better distributed. The median between the two is almost the same.

9.
```{r}

female <- tips[tips$sex == "Female",  ]
male <- tips[tips$sex == "Male",  ]

my_plot <- ggplot(data=female, aes(x=total_bill, y=tip, color=smoker))
my_plot + geom_point()

my_plot <- ggplot(data=male, aes(x=total_bill, y=tip, color=smoker))
my_plot + geom_point()

```
A lot of the females had lower bills, which meant less tips.

Women who are smokers appear to tip less than women who are not smokers. There does not appear to be much of a correlation for men in regards to if they smoke or not when paying

10.
```{r}
my_plot <- ggplot(data=tips, aes(x=tips$day, fill=tips$sex))

my_plot + geom_bar()
```

Men are more likely to pay the bill on Saturday and Sunday. Women are more likely to pay on Thursdays. On Fridays men and women both are as likely to pay the bill as the other person.