---
title: "R Notebook"
output:
  html_document:
    df_print: paged
name: Ann Gould
---


```{r}
data(tips, package="reshape2")
library(dplyr)
library(ggplot2)

```

1. 
```{r}
numParty <- nrow(tips)
print(numParty)
```

2. 
```{r}
print(tips)
print(names(tips))
```
total_bill: total sum of bill
tip: tip included 
size: # of people in party
sex: gender of waiter/waitress
smoker: if the waiter/waitress smoked
day: day of the week going out
time: specific meal

3.
```{r}
newdata <- tips[order(tips$day, decreasing = TRUE),] 
print(newdata)
```

4.
```{r}
data <- tips %>%
  group_by(sex) %>%
  summarise(day_visits = sum(total_bill))
print(data)
  
```
5.
```{r}
plot(tips)

```

The lower the bill, the lower the tip typically and vice versa. Linear regression-like line.

6.
There is a lot of data in the lower aspect of the graph, which makes it more difficult to predict later data. There also exists some outliers of people who tip really well/very poorly.

7.
```{r}
data <- tips %>%
  summarise(tiprate = mean(tip))
print(data)
```
The average tip for the dataset is 2.998279.


